---
title: "TellME Europe DGVMTools Benchmarking"
author: "Karl Piltz"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true  # Optional: Table of Contents
    toc_depth: 2  # Optional: Adjust TOC depth
    toc_float: true  # Optional: Floating TOC
---
```{r setup, include=FALSE}
library(ggplot2)
theme_set(theme_bw())
library(DGVMBenchmarks)
library(DGVMTools)
library(knitr)
library(dplyr)
library(tidyr)
library(tidyverse)
library(kableExtra)
library(tictoc)
library(ggpubr)
library(yaml)
library(showtext) 
library(data.table)
library(patchwork)
library(extrafont) 
library(ggthemes)
library(ggrepel)
library(sf)
library(units)
library(RColorBrewer)
library(flextable)
library(readxl)
showtext_auto()
# start timer
tic()
```
# Settings {.tabset}

## Hide settings

## Show settings
```{r settings,  echo=F, warning=FALSE}
source(file.path("C:\\Users\\Admin\\Documents\\tellus\\TellMeEurope_Set_Ups\\European_applications\\TellMeEurope_config.R"))  

str(input, max.level = 4)

# plot maps (turn off to save time)
do_plots <- as.logical(input[["Switches"]][["do_plots"]])

## NFI Switches
do_agpp <- as.logical(input[["Switches"]][["do_agpp"]])
do_cmass <- as.logical(input[["Switches"]][["do_cmass"]]) 
do_stem_density <- as.logical(input[["Switches"]][["do_stem_density"]])
do_qdbh <- as.logical(input[["Switches"]][["do_qdbh"]])
do_woody_growth <- as.logical(input[["Switches"]][["do_woody_growth"]])
do_cmass_pft <- as.logical(input[["Switches"]][["do_cmass_pft"]])
do_cmass_pft1 <- as.logical(input[["Switches"]][["do_cmass_pft1"]])


## Regrowth Switch
do_Regrowth <- as.logical(input[["Switches"]][["do_Regrowth"]])

## Storm Switch
do_storm <- as.logical(input[["Switches"]][["do_storm"]])

## Fire Switches
do_SIMFIRE <- as.logical(input[["Switches"]][["do_SIMFIRE"]])
do_BLAZE <- as.logical(input[["Switches"]][["do_BLAZE"]])

## ICOS Switches
do_ICOS_GPP <- as.logical(input[["Switches"]][["do_ICOS_GPP"]])
do_ICOS_NEE <- as.logical(input[["Switches"]][["do_ICOS_NEE"]])
do_ICOS_Reco <- as.logical(input[["Switches"]][["do_ICOS_Reco"]])
do_ICOS_ET <- as.logical(input[["Switches"]][["do_ICOS_ET"]])

## FLUXNET Switches
do_FLUXNET_GPP <- as.logical(input[["Switches"]][["do_FLUXNET_GPP"]])
do_FLUXNET_NEE <- as.logical(input[["Switches"]][["do_FLUXNET_NEE"]])
do_FLUXNET_Reco <- as.logical(input[["Switches"]][["do_FLUXNET_Reco"]])
plot_combined <- FALSE

```
***

# Fire {.tabset}

## Burnt Area 
```{r Difference1, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_SIMFIRE){
  # Define which benchmark to do
benchmark_name <- "Burnt_area"

# Process your dataset
Datasets <- processDataSource(all_datasets = all_datasets, input, spatial.extent = spatial.extent, benchmark_name)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_sim_full[[1]]@data$BurntFr <- all_sim_full[[1]]@data$BurntFr * 100


## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,new_model = all_sim_full[[1]]@source@name)

## Spatial plotting of your comparisons, handels multiple layers to.
if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons, type = "difference")}

## Table making, extracts the spatial mean from your fields.
summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## Burnt Area table 
```{r Difference2, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
if (do_SIMFIRE){
  # Define which benchmark to do
benchmark_name <- "Burnt_area_table"

gridcell_area <- read_table('C:\\Users\\Admin\\Documents\\tellus\\Fire_runs_2026-08-18\\Gridcell_areas_EuroApp_gridlist.txt')

# Process your dataset
Datasets <- processDataSource(all_datasets = all_datasets, input, spatial.extent = spatial.extent, benchmark_name)
Datasets[[1]]@data <- merge(
  Datasets[[1]]@data,
  gridcell_area[, c("lons", "lats", "A")],
  by.x = c("Lon", "Lat"),
  by.y = c("lons", "lats"),
  all.x = TRUE
)
Datasets[[1]]@data[, A := A / 1e6]
Datasets[[1]]@data$BurntFr <- Datasets[[1]]@data$BurntFr * Datasets[[1]]@data$A
Datasets[[1]]@data <- Datasets[[1]]@data %>%
  dplyr::select(-A)
# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]


all_sim_full[[1]]@data <- merge(
  all_sim_full[[1]]@data,
  gridcell_area[, c("lons", "lats", "A")],
  by.x = c("Lon", "Lat"),
  by.y = c("lons", "lats"),
  all.x = TRUE
)
all_sim_full[[1]]@data[, A := A / 1e6]
all_sim_full[[1]]@data$BurntFr <- all_sim_full[[1]]@data$BurntFr * all_sim_full[[1]]@data$A
all_sim_full[[1]]@data <- all_sim_full[[1]]@data %>%
  dplyr::select(-A)



Fire_table <- FireTable(all_sim_full = all_sim_full, new_model = all_sim_full[[1]]@source@name)


Fire_table %>%
  kable(
    format = "html",
    digits = 6,
    caption = "Annual burnt area (km^2/yr)"
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "center"
  ) %>%
  row_spec(0, bold = TRUE)

}
```

## Fire C emissions 
```{r Fire C emissions, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_SIMFIRE){
  # Define which benchmark to do
benchmark_name <- "Fire_C_emissions"

gridcell_area <- read_table('C:\\Users\\Admin\\Documents\\tellus\\Fire_runs_2026-08-18\\Gridcell_areas_EuroApp_gridlist.txt')
# Process your dataset
Datasets <- processDataSource(all_datasets = all_datasets, input, spatial.extent = spatial.extent, benchmark_name)


 Datasets[[1]]@data$Fire <- Datasets[[1]]@data$Fire * 1e3

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]



 all_Fields_list[[2]]@data$Fire <- all_Fields_list[[2]]@data$Fire * 1e3


## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,new_model = all_sim_full[[1]]@source@name)

## Spatial plotting of your comparisons, handels multiple layers to.
if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons, type = "difference")}

## Table making, extracts the spatial mean from your fields.
summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## Fire C emissions table 
```{r Fire C emissions2, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
if (do_SIMFIRE){
  # Define which benchmark to do
benchmark_name <- "Fire_C_emissions_table"

gridcell_area <- read_table('C:\\Users\\Admin\\Documents\\tellus\\Fire_runs_2026-08-18\\Gridcell_areas_EuroApp_gridlist.txt')

# Process your dataset
Datasets <- processDataSource(all_datasets = all_datasets, input, spatial.extent = spatial.extent, benchmark_name)
Datasets[[1]]@data <- merge(
  Datasets[[1]]@data,
  gridcell_area[, c("lons", "lats", "A")],
  by.x = c("Lon", "Lat"),
  by.y = c("lons", "lats"),
  all.x = TRUE
)

Datasets[[1]]@data$Fire <- Datasets[[1]]@data$Fire * Datasets[[1]]@data$A / 1e3
Datasets[[1]]@data <- Datasets[[1]]@data %>%
  dplyr::select(-A)
Datasets[[1]]@data$Fire <- Datasets[[1]]@data$Fire / 1e3


# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]


all_sim_full[[1]]@data <- merge(
  all_sim_full[[1]]@data,
  gridcell_area[, c("lons", "lats", "A")],
  by.x = c("Lon", "Lat"),
  by.y = c("lons", "lats"),
  all.x = TRUE
)
all_sim_full[[1]]@data$Fire <- all_sim_full[[1]]@data$Fire * all_sim_full[[1]]@data$A / 1e3
all_sim_full[[1]]@data <- all_sim_full[[1]]@data %>%
  dplyr::select(-A)
all_sim_full[[1]]@data$Fire <- all_sim_full[[1]]@data$Fire / 1e3


Fire_table <- FireTable(all_sim_full = all_sim_full, new_model = all_sim_full[[1]]@source@name)


Fire_table %>%
  kable(
    format = "html",
    digits = 6,
    caption = "Fire C emissions (Mg C km⁻² yr⁻¹)"
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "center"
  ) %>%
  row_spec(0, bold = TRUE)

}
```


# Storm {.tabset}

## Storm disturbance
```{r Storm, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_storm){
benchmark_name <- "STORM"

# Process your dataset
Datasets <- processDataSource(all_datasets = all_datasets, input, spatial.extent = spatial.extent, benchmark_name)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

plotStormMap(benchmark = this_benchmark,all_sim_full = all_sim_full, LC = LC)
}
```

## Storm Scatter
```{r Storm scatter, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_storm){
benchmark_name <- "STORM"

# Process your dataset
Datasets <- processDataSource(all_datasets = all_datasets, input, spatial.extent = spatial.extent, benchmark_name)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

plotStormScatter(benchmark = this_benchmark,all_sim_full = all_sim_full,do_plots = do_plots, LC = LC)
}
```

## Storm Table
```{r Storm Table, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
if (do_storm){
benchmark_name <- "STORM"

# Process your dataset
Datasets <- processDataSource(all_datasets = all_datasets, input, spatial.extent = spatial.extent, benchmark_name)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

storm_table <- plotStormScatter(benchmark = this_benchmark,all_sim_full = all_sim_full, do_plots = FALSE, LC = LC)


storm_table %>%
  kable(
    format = "html",
    digits = 6,
    caption = "Total reported & modelled wind damage"
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "center"
  ) %>%
  row_spec(0, bold = TRUE)

}
```


# AGPP {.tabset}

## AGPP difference Plots 
```{r Difference, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_agpp){
  # Define which benchmark to do
benchmark_name <- "AGPP1"

# Process your dataset
Datasets <- processDataSource(all_datasets = all_datasets, input, spatial.extent = spatial.extent, benchmark_name)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name , old_model = all_sim_full[[2]]@source@name)

## Spatial plotting of your comparisons, handels multiple layers to.
if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons, type = "difference")}

## Table making, extracts the spatial mean from your fields.
summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## AGPP Scatterplots 
```{r AGPP_SCATTER, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_plots && do_agpp){DGVMBenchmarks::plotFullScatter(Benchmark = this_benchmark, all_sim_full = all_sim_full)}
```

## AGPP Relative difference 
```{r AGPP_Relative, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_agpp){ 
all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)
 if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons, type = "percentage.difference")}}

```

# Cmass {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["CMASS1"]][["Data"]][["Dataset_description"]])
```

## Cmass Difference plots
```{r Cmass, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_cmass){
benchmark_name <- "CMASS1"
  
Datasets <- processDataSource(all_datasets = all_datasets, input, benchmark_name, spatial.extent = spatial.extent)

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}

summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)

if(length(this_benchmark@datasets) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}

}
```

## Cmass Scatterplots
```{r cmass scatter, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if(do_plots && do_cmass){DGVMBenchmarks::plotFullScatter(Benchmark = this_benchmark, all_sim_full = all_sim_full)}
```


## Cmass Relative difference 
```{r Cmass_Relative, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_cmass){
all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name) 
if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons, type = "percentage.difference", percentile_limit = 90)}}

```


# Stem Density {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["STEM_DENSITY1"]][["Data"]][["Dataset_description"]])
```

## Difference 
```{r Stemdensity, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_stem_density){
benchmark_name <- "STEM_DENSITY1"

Datasets <- processDataSource(all_datasets = all_datasets, input, benchmark_name,spatial.extent = spatial.extent)

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark, all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]
all_sim_full[[1]]@data$Forest_sum <- all_sim_full[[1]]@data$Forest_sum*10000 # convertUnits(all_sim_full[[2]],"indiv/m2","indiv/ha")
all_sim_full[[2]]@data$Forest_sum <- all_sim_full[[2]]@data$Forest_sum*10000 #convertUnits(all_sim_full[[1]],"indiv/m2","indiv/ha")
all_Fields_list[[2]]@data$Forest_sum <- all_Fields_list[[2]]@data$Forest_sum*10000 #convertUnits(all_Fields_list[[1]],"indiv/m2","indiv/ha")
all_Fields_list[[3]]@data$Forest_sum <- all_Fields_list[[3]]@data$Forest_sum*10000 #convertUnits(all_Fields_list[[2]],"indiv/m2","indiv/ha")

all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}

summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)
if(length(this_benchmark@datasets) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## Stem Density Scatterplots
```{r Stemdensity scatter, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if(do_plots && do_stem_density){DGVMBenchmarks::plotFullScatter(Benchmark = this_benchmark, all_sim_full = all_sim_full)}
```

## Density Relative difference 
```{r dens_Relative, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_cmass){
all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name) 
if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons, type = "percentage.difference", percentile_limit = 90)}}

```

# QDBH {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["QDBH1"]][["Data"]][["Dataset_description"]])
```

## QDBH Difference
```{r QDBH, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_qdbh){
benchmark_name <- "QDBH1"

Datasets <- processDataSource(all_datasets = all_datasets, input, benchmark_name, spatial.extent = spatial.extent)

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}

summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)
if(length(this_benchmark@datasets) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## QDBH Scatterplots
```{r QDBH Scatter, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if(do_plots && do_qdbh){DGVMBenchmarks::plotFullScatter(Benchmark = this_benchmark, all_sim_full = all_sim_full)}
```

## QDBH Relative difference 
```{r QDBH_Relative, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_qdbh){
all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name) 
if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons, type = "percentage.difference", percentile_limit = 90)}}

```

# Woody Growth {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["W_GROWTH1"]][["Data"]][["Dataset_description"]])
```

## Woody Growth Difference
```{r Woody growth difference, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_woody_growth){
benchmark_name <- "W_GROWTH1" 

Datasets <- processDataSource(all_datasets = all_datasets, input, benchmark_name, spatial.extent = spatial.extent)

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}

summary_table <- DGVMBenchmarks::buildSummaryTable(benchmark = this_benchmark, all_sim_full, summary_col_names, input = input)

if(length(this_benchmark@datasets) != 0){metric_table <- rbind(metric_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}


}
```

## Woody Growth Scatter
```{r Woody growth scatter, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if(do_plots && do_woody_growth){DGVMBenchmarks::plotFullScatter(Benchmark = this_benchmark, all_sim_full = all_sim_full)}
```

## Woody Growth Relative difference 
```{r wg_Relative, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
if (do_woody_growth){
all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name) 
if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons, type = "percentage.difference", percentile_limit = 90)}}

```

# PFT CMASS {.tabset}

```{r, echo = FALSE, eval = TRUE, results = "asis"}
cat(input[["CMASS_pft1"]][["Data"]][["Dataset_description"]])
```

## Difference

```{r pft cmass difference, echo=FALSE, message=FALSE, warning=FALSE, results='hide',out.width = "120%",out.height="120%"}
if (do_cmass_pft){
benchmark_name <- "CMASS_pft1" 

Datasets <- list()

this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark, all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

all_comparisons <- DGVMBenchmarks::fullSpatialComparison(benchmark = this_benchmark, all_maps = all_Fields_list,       new_model = all_sim_full[[1]]@source@name, old_model = all_sim_full[[2]]@source@name)

if(do_plots){DGVMBenchmarks::plotAllSpatialComparisons(Benchmark = this_benchmark, all_comparisons = all_comparisons)}
}
```



## Total PFT Cmass

```{r pft cmass, echo=FALSE, message=FALSE, warning=FALSE, results='hide',out.width = "120%",out.height="120%"}
do_cmass_pft1 <- TRUE
if (do_cmass_pft1){
benchmark_name <- "CMASS_pft1" 

Data.year.mean <- list()

this_benchmark <- createBenchmark(benchmark_name, input, Data.year.mean, spatial.extent)

field_lists <- DGVMBenchmarks::getAllFields(this_benchmark, all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

if(do_plots){plotSpatialField(Benchmark = this_benchmark, all_Fields_list = all_Fields_list)}
}
```

# Summary table spatial mean
```{r Summary table, echo=FALSE, message=FALSE, warning=FALSE}
 if(nrow(summary_table) > 0) {
   kable(summary_table) %>% kable_styling(full_width = TRUE)}
```

# Model-data Agreement Metrics 
```{r Metric table, echo=FALSE, message=FALSE, warning=FALSE}
if(nrow(metric_table) > 0) {
   #substitute "r2" for something prettier in the "Metric" column
  metric_table$Metric <- gsub(pattern = "r2", replacement = "R^2^", metric_table$Metric)
  #metric_table$input[["Directory"]][["New_id"]] <- as.numeric(metric_table$input[["Directory"]][["New_id"]])
  #metric_table$input[["Directory"]][["New_id"]] <- sprintf("%.3f", metric_table$input[["Directory"]][["New_id"]])
   #print the table
  kable(metric_table) %>% kable_styling(full_width = TRUE)}
```


# ICOS bias corrected GPP {.tabset}

## Daily Total
```{r ICOS GPP, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=18, fig.height=14}
if (do_ICOS_GPP){
  # Define which benchmark to do
benchmark_name <- "ICOS_GPP1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name = benchmark_name)

Datasets <- correctFLUXNETDataset(Datasets)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]


## Account for missmatch between coords in LPJ-GUESS grid and ICOS stations
#FLUXNET_grid <- read.table(file.path(system.file("/Users/filipegmsalmeida/Downloads/FLUXNET/Fluxnet_grid.txt", package = "DGVMBenchmarks")))

ICOS_grid <- read.table(
  "/Users/filipegmsalmeida/Library/CloudStorage/OneDrive-Personal/lpj_guess/simulations/european_applications_benchemark/TELL_ME_ICOS_FLUXNET/ICOS_grid.txt",
  header = TRUE,
  sep = "\t",
  quote = "\"",
  stringsAsFactors = FALSE
)

#FLUXNET_grid <- FLUXNET_grid[FLUXNET_grid$Code != "IT-La2", ]
# Merge By Station name in ICOS Data      
merged_data <- merge(all_Fields_list[[1]]@data, ICOS_grid, 
                                by = c("Code", "Name"), 
                                all = TRUE)


merged_data[, `:=`(
  Lat = GUESS_Lat,
  Lon = GUESS_Lon
)]

all_Fields_list[[1]]@data <- merged_data[!is.na(Lat) & !is.na(Lon)]

this_benchmark@datasets[[1]]@data <- all_Fields_list[[1]]@data


 #all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data[!( (Lat == 42.25 & Lon == 116.25)), ]
 lats <- unique(all_Fields_list[[1]]@data$Lat)
 lons <- unique(all_Fields_list[[1]]@data$Lon)

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name)
plotICOSFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
#plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"per_source")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){ICOS_table <- rbind(ICOS_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}

this_benchmark_gpp <- this_benchmark
all_comparisons_gpp <- all_comparisons
```

## Daily Difference
```{r Difference ICOS GPP, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=18, fig.height=14}
if (do_ICOS_GPP){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```


## GPP per site
```{r per site ICOS GPP, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=9, fig.height=7}
if (do_ICOS_GPP){plotICOSScatter(this_benchmark,all_comparisons,fill="station")}
```

## GPP per Land cover
```{r per lc ICOS GPP, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=9, fig.height=7}
if (do_ICOS_GPP){plotICOSScatter(this_benchmark,all_comparisons,fill="landcover")}
```


# ICOS bias corrected NEE {.tabset}


## Daily Total
```{r ICOS NEE, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=18, fig.height=14}
if (do_ICOS_NEE){
  # Define which benchmark to do
benchmark_name <- "ICOS_NEE1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name = benchmark_name)

Datasets <- correctFLUXNETDataset(Datasets)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]


## Account for missmatch between coords in LPJ-GUESS grid and ICOS stations
#FLUXNET_grid <- read.table(file.path(system.file("/Users/filipegmsalmeida/Downloads/FLUXNET/Fluxnet_grid.txt", package = "DGVMBenchmarks")))

ICOS_grid <- read.table(
  "/Users/filipegmsalmeida/Library/CloudStorage/OneDrive-Personal/lpj_guess/simulations/european_applications_benchemark/TELL_ME_ICOS_FLUXNET/ICOS_grid.txt",
  header = TRUE,
  sep = "\t",
  quote = "\"",
  stringsAsFactors = FALSE
)

merged_data <- merge(all_Fields_list[[1]]@data, ICOS_grid, 
                                by = c("Code", "Name"), 
                                all = TRUE)


merged_data[, `:=`(
  Lat = GUESS_Lat,
  Lon = GUESS_Lon
)]

all_Fields_list[[1]]@data <- merged_data[!is.na(Lat) & !is.na(Lon)]

this_benchmark@datasets[[1]]@data <- all_Fields_list[[1]]@data

 #all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data[!( (Lat == 42.25 & Lon == 116.25)), ]
 lats <- unique(all_Fields_list[[1]]@data$Lat)
 lons <- unique(all_Fields_list[[1]]@data$Lon)

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name)
plotICOSFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
#plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"per_source")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){ICOS_table <- rbind(ICOS_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}

this_benchmark_nee <- this_benchmark
all_comparisons_nee <- all_comparisons
```


## NEE Daily Difference
```{r Difference ICOS NEE, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=18, fig.height=14}
if (do_ICOS_NEE){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```

## NEE per site
```{r per site ICOS NEE, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=9, fig.height=7}
if (do_ICOS_NEE){plotICOSScatter(this_benchmark,all_comparisons,fill="station")}
```

## NEE per Land cover
```{r per lc ICOS NEE, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=9, fig.height=7}
if (do_ICOS_NEE){plotICOSScatter(this_benchmark,all_comparisons,fill="landcover")}
```

# ICOS bias corrected Reco {.tabset}

## Daily Total
```{r ICOS Reco, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=18, fig.height=14}
if (do_ICOS_Reco){
  # Define which benchmark to do
benchmark_name <- "ICOS_Reco1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name = benchmark_name)

Datasets <- correctFLUXNETDataset(Datasets)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]


## Account for missmatch between coords in LPJ-GUESS grid and ICOS stations
#FLUXNET_grid <- read.table(file.path(system.file("/Users/filipegmsalmeida/Downloads/FLUXNET/Fluxnet_grid.txt", package = "DGVMBenchmarks")))

ICOS_grid <- read.table(
  "/Users/filipegmsalmeida/Library/CloudStorage/OneDrive-Personal/lpj_guess/simulations/european_applications_benchemark/TELL_ME_ICOS_FLUXNET/ICOS_grid.txt",
  header = TRUE,
  sep = "\t",
  quote = "\"",
  stringsAsFactors = FALSE
)

merged_data <- merge(all_Fields_list[[1]]@data, ICOS_grid, 
                                by = c("Code", "Name"), 
                                all = TRUE)


merged_data[, `:=`(
  Lat = GUESS_Lat,
  Lon = GUESS_Lon
)]

all_Fields_list[[1]]@data <- merged_data[!is.na(Lat) & !is.na(Lon)]

this_benchmark@datasets[[1]]@data <- all_Fields_list[[1]]@data

 all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data[!( (Lat == 42.25 & Lon == 116.25)), ]
 lats <- unique(all_Fields_list[[1]]@data$Lat)
 lons <- unique(all_Fields_list[[1]]@data$Lon)

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name)
plotICOSFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
#plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"per_source")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){ICOS_table <- rbind(ICOS_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}

this_benchmark_reco <- this_benchmark
all_comparisons_reco <- all_comparisons
```


## Reco Daily Difference
```{r Difference ICOS Reco, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=18, fig.height=14}
if (do_ICOS_Reco){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```


## Reco per site
```{r per site ICOS Reco, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=9, fig.height=7}
if (do_ICOS_Reco){plotICOSScatter(this_benchmark,all_comparisons,fill="station")}
```

## Reco per Land cover
```{r per lc ICOS Reco, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=9, fig.height=7}
if (do_ICOS_Reco){plotICOSScatter(this_benchmark,all_comparisons,fill="landcover")}
```

# ICOS bias corrected ET {.tabset}

## Daily Total
```{r ICOS ET, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=18, fig.height=14}
if (do_ICOS_ET){
  # Define which benchmark to do
benchmark_name <- "ICOS_ET1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name = benchmark_name)

# Convert Latent heat flux to Evapotranspiration from W/m^2 -> mm/day
latent_heat_of_vaporization <- 2.45
Datasets[["ICOS"]]@data$ET <- (Datasets[["ICOS"]]@data$ET * 86400) / (latent_heat_of_vaporization * 1e6)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]

## Account for missmatch between coords in LPJ-GUESS grid and ICOS stations
#FLUXNET_grid <- read.table(file.path(system.file("/Users/filipegmsalmeida/Downloads/FLUXNET/Fluxnet_grid.txt", package = "DGVMBenchmarks")))

ICOS_grid <- read.table(
  "/Users/filipegmsalmeida/Library/CloudStorage/OneDrive-Personal/lpj_guess/simulations/european_applications_benchemark/TELL_ME_ICOS_FLUXNET/ICOS_grid.txt",
  header = TRUE,
  sep = "\t",
  quote = "\"",
  stringsAsFactors = FALSE
)

#FLUXNET_grid <- FLUXNET_grid[FLUXNET_grid$Code != "IT-La2", ]
# Merge By Station name in ICOS Data      
merged_data <- merge(all_Fields_list[[1]]@data, ICOS_grid, 
                                by = c("Code", "Name"), 
                                all = TRUE)


merged_data[, `:=`(
  Lat = GUESS_Lat,
  Lon = GUESS_Lon
)]

all_Fields_list[[1]]@data <- merged_data[!is.na(Lat) & !is.na(Lon)]

this_benchmark@datasets[[1]]@data <- all_Fields_list[[1]]@data


 #all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data[!( (Lat == 42.25 & Lon == 116.25)), ]
 lats <- unique(all_Fields_list[[1]]@data$Lat)
 lons <- unique(all_Fields_list[[1]]@data$Lon)

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name)
plotICOSFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
#plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"per_source")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){ICOS_table <- rbind(ICOS_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}

this_benchmark_et <- this_benchmark
all_comparisons_et <- all_comparisons
```

## Daily Difference
```{r Difference ICOS ET, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=18, fig.height=14}
if (do_ICOS_ET){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```


## GPP per site
```{r per site ICOS ET, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=9, fig.height=7}
if (do_ICOS_ET){plotICOSScatter(this_benchmark,all_comparisons,fill="station")}
```

## GPP per Land cover
```{r per lc ICOS ET, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=9, fig.height=7}
if (do_ICOS_ET){plotICOSScatter(this_benchmark,all_comparisons,fill="landcover")}
```



# ICOS metric table
```{r ICOS Metric table, echo=FALSE, message=FALSE, warning=FALSE}
if(nrow(ICOS_table) > 0) {
   #substitute "r2" for something prettier in the "Metric" column
  ICOS_table$Metric <- gsub(pattern = "r2", replacement = "R^2^", ICOS_table$Metric)
  
   #print the table
  kable(ICOS_table) %>% kable_styling(full_width = TRUE)}
```

```{r ICOS combined plot, echo=FALSE, message=FALSE, warning=FALSE}
if (plot_combined)
  library(ggplot2)
  library(patchwork)
  
  # ------------------------------------------------------------
  # 1. CREATE THE FOUR PLOTS
  # ------------------------------------------------------------
  
  p_gpp <- plotICOSScatter(
    this_benchmark_gpp,
    all_comparisons_gpp,
    fill = "station"
  ) +
    labs(
      x = expression("ICOS GPP (kg C "*m^{-2}*" day"^{-1}*")"),
      y = expression("Model GPP (kg C "*m^{-2}*" day"^{-1}*")")
    )
  
  p_nee <- plotICOSScatter(
    this_benchmark_nee,
    all_comparisons_nee,
    fill = "station"
  ) +
    labs(
      x = expression("ICOS NEE (kg C "*m^{-2}*" day"^{-1}*")"),
      y = expression("Model NEE (kg C "*m^{-2}*" day"^{-1}*")")
    )
  
  p_reco <- plotICOSScatter(
    this_benchmark_reco,
    all_comparisons_reco,
    fill = "station"
  ) +
    labs(
      x = expression("ICOS Reco (kg C "*m^{-2}*" day"^{-1}*")"),
      y = expression("Model Reco (kg C "*m^{-2}*" day"^{-1}*")")
    )
  
  p_et <- plotICOSScatter(
    this_benchmark_et,
    all_comparisons_et,
    fill = "station"
  ) +
    labs(
      x = expression("ICOS ET (mm day"^{-1}*")"),
      y = expression("Model ET (mm day"^{-1}*")")
    )
  
  
  # ------------------------------------------------------------
  # 2. COMMON THEME
  # ------------------------------------------------------------
  
  common_theme <- theme(
    plot.title = element_blank(),
  
    axis.title.x = element_text(
      size = 16,
      margin = margin(t = 5)
    ),
  
    axis.title.y = element_text(
      size = 16,
      margin = margin(r = 5)
    ),
  
    axis.text.x = element_text(
      size = 11
    ),
  
    axis.text.y = element_text(
      size = 11
    ),
  
    plot.margin = margin(2, 2, 2, 2)
  )
  
  
  # ------------------------------------------------------------
  # 3. APPLY THEME
  # ------------------------------------------------------------
  
  p_gpp <- p_gpp + common_theme
  p_nee <- p_nee + common_theme
  p_reco <- p_reco + common_theme
  p_et <- p_et + common_theme
  
  
  # ------------------------------------------------------------
  # 4. REMOVE DUPLICATE LEGEND + SET LEGEND FORMAT
  # ------------------------------------------------------------
  
  p_gpp <- p_gpp +
    guides(
      fill = "none",   # removes duplicate station legend
  
      color = guide_legend(
        title = "Stations",
        ncol = 2,
        order = 2
      ),
  
      shape = guide_legend(
        title = "Season",
        ncol = 4,
        order = 1,
        title.position = "top",
        title.hjust = 0.5
      )
    )
  
  p_nee <- p_nee +
    guides(fill = "none")
  
  p_reco <- p_reco +
    guides(fill = "none")
  
  p_et <- p_et +
    guides(fill = "none")
  
  
  # ------------------------------------------------------------
  # 5. COMBINE PLOTS AND COLLECT LEGENDS
  # ------------------------------------------------------------
  
  final <- (
    p_gpp + p_nee +
    p_reco + p_et
  ) +
    plot_layout(
      ncol = 2,
      guides = "collect"
    ) &
    theme(
  
      # -----------------------
      # AXIS TITLES
      # -----------------------
      axis.title.x = element_text(
        size = 30,
        margin = margin(t = 8)
      ),
  
      axis.title.y = element_text(
        size = 30,
        margin = margin(r = 8)
      ),
  
      # -----------------------
      # AXIS NUMBERS
      # -----------------------
      axis.text.x = element_text(
        size = 27
      ),
  
      axis.text.y = element_text(
        size = 27
      ),
  
      # -----------------------
      # LEGEND
      # -----------------------
      legend.position = "right",
  
      legend.title = element_text(
        size = 30,
        face = "bold"
      ),
  
      legend.text = element_text(
        size = 27
      ),
  
      legend.key.height = unit(0.45, "cm"),
      legend.key.width = unit(0.40, "cm"),
  
      legend.spacing.y = unit(0.05, "cm"),
      legend.spacing.x = unit(0.10, "cm"),
  
      legend.margin = margin(0, 0, 0, 0),
      legend.box.margin = margin(0, 0, 0, 0),
  
      plot.margin = margin(4, 4, 4, 4)
    )
  
  final
  # ------------------------------------------------------------
  # 6. SAVE
  # ------------------------------------------------------------
  
  ggsave(
    "/Users/filipegmsalmeida/Library/CloudStorage/OneDrive-Personal/lpj_guess/simulations/european_applications_benchemark/TELL_ME_ICOS_FLUXNET/ICOS_combined_final.png",
    plot = final,
    width = 14,
    height = 9,
    units = "in",
    dpi = 300,
    bg = "white"
  )
```


# FLUXNET bias corrected GPP {.tabset}

## Daily Total
```{r FLUXNET GPP, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=18, fig.height=14}
if (do_FLUXNET_GPP){
  # Define which benchmark to do
benchmark_name <- "FLUXNET_GPP1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name = benchmark_name)

Datasets <- correctFLUXNETDataset(Datasets)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]


## Account for missmatch between coords in LPJ-GUESS grid and ICOS stations
#FLUXNET_grid <- read.table(file.path(system.file("/Users/filipegmsalmeida/Downloads/FLUXNET/Fluxnet_grid.txt", package = "DGVMBenchmarks")))

FLUXNET_grid <- read.table(
  "/Users/filipegmsalmeida/Library/CloudStorage/OneDrive-Personal/lpj_guess/simulations/european_applications_benchemark/TELL_ME_ICOS_FLUXNET/Fluxnet_grid_european_applications.txt",
  header = TRUE,
  sep = "\t",
  quote = "\"",
  stringsAsFactors = FALSE
)

FLUXNET_grid <- FLUXNET_grid[FLUXNET_grid$Code != "IT-La2", ]
# Merge By Station name in ICOS Data      
merged_data <- merge(all_Fields_list[[1]]@data, FLUXNET_grid, 
                                by = c("Code", "Name"), 
                                all = TRUE)

merged_data[, `:=`(
  Lat = GUESS_Lat,
  Lon = GUESS_Lon
)]

all_Fields_list[[1]]@data <- merged_data[!is.na(Lat) & !is.na(Lon)]

this_benchmark@datasets[[1]]@data <- all_Fields_list[[1]]@data

 #all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data[!( (Lat == 42.25 & Lon == 116.25)), ]
 lats <- unique(all_Fields_list[[1]]@data$Lat)
 lons <- unique(all_Fields_list[[1]]@data$Lon)

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name)
plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
#plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"per_source")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){FLUXNET_table <- rbind(FLUXNET_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```

## Daily Difference
```{r Difference Flux GPP, echo=FALSE, message=FALSE, warning=FALSE, results='hide',  fig.width=18, fig.height=14}
if (do_FLUXNET_GPP){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```


## GPP per site
```{r per site flux GPP, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=16, fig.height=12}
if (do_FLUXNET_GPP){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="station")}
```

## GPP per Land cover
```{r per lc flux GPP, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=14, fig.height=10}
if (do_FLUXNET_GPP){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="landcover")}
```


# FLUXNET bias corrected NEE {.tabset}


## Daily Total
```{r FLUXNET NEE, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=18, fig.height=14}
if (do_FLUXNET_NEE){
  # Define which benchmark to do
benchmark_name <- "FLUXNET_NEE1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name = benchmark_name)

#Datasets <- correctFLUXNETDataset(Datasets)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]


## Account for missmatch between coords in LPJ-GUESS grid and ICOS stations
#FLUXNET_grid <- read.table(file.path(system.file("/Users/filipegmsalmeida/Downloads/FLUXNET/Fluxnet_grid.txt", package = "DGVMBenchmarks")))

FLUXNET_grid <- read.table(
  "/Users/filipegmsalmeida/Library/CloudStorage/OneDrive-Personal/lpj_guess/simulations/european_applications_benchemark/TELL_ME_ICOS_FLUXNET/Fluxnet_grid_european_applications.txt",
  header = TRUE,
  sep = "\t",
  quote = "\"",
  stringsAsFactors = FALSE
)

FLUXNET_grid <- FLUXNET_grid[FLUXNET_grid$Code != "IT-La2", ]
# Merge By Station name in ICOS Data      
merged_data <- merge(all_Fields_list[[1]]@data, FLUXNET_grid, 
                                by = c("Code", "Name"), 
                                all = TRUE)

merged_data[, `:=`(
  Lat = GUESS_Lat,
  Lon = GUESS_Lon
)]

all_Fields_list[[1]]@data <- merged_data[!is.na(Lat) & !is.na(Lon)]

this_benchmark@datasets[[1]]@data <- all_Fields_list[[1]]@data

 #all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data[!( (Lat == 42.25 & Lon == 116.25)), ]
 lats <- unique(all_Fields_list[[1]]@data$Lat)
 lons <- unique(all_Fields_list[[1]]@data$Lon)

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name)
plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
#plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"per_source")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){FLUXNET_table <- rbind(FLUXNET_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```


## NEE Daily Difference
```{r Difference Flux NEE, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=18, fig.height=14}
if (do_FLUXNET_NEE){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```


## NEE per site
```{r per site flux NEE, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=16, fig.height=12}
if (do_FLUXNET_NEE){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="station")}
```

## NEE per Land cover
```{r per lc flux NEE, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=14, fig.height=10}
if (do_FLUXNET_NEE){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="landcover")}
```

# FLUXNET bias corrected Reco {.tabset}

## Daily Total
```{r FLUXNET Reco, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=18, fig.height=14}
if (do_FLUXNET_Reco){
  # Define which benchmark to do
benchmark_name <- "FLUXNET_Reco1"

# Process your dataset
Datasets <- processDataSource(all_datasets, input, spatial.extent = spatial.extent, benchmark_name = benchmark_name)

Datasets <- correctFLUXNETDataset(Datasets)

# Build your current benchmark from input YAML file  
this_benchmark <- createBenchmark(benchmark_name, input, Datasets = Datasets, spatial.extent)

# Process simulations and order together with dataset, the lists returned are needed in later functions.
field_lists <- DGVMBenchmarks::getAllFields(this_benchmark,all_simulation_Sources_list)
all_sim_full <- field_lists[[1]]
all_Fields_list <- field_lists[[2]]


## Account for missmatch between coords in LPJ-GUESS grid and ICOS stations
#FLUXNET_grid <- read.table(file.path(system.file("/Users/filipegmsalmeida/Downloads/FLUXNET/Fluxnet_grid.txt", package = "DGVMBenchmarks")))

FLUXNET_grid <- read.table(
  "/Users/filipegmsalmeida/Library/CloudStorage/OneDrive-Personal/lpj_guess/simulations/european_applications_benchemark/TELL_ME_ICOS_FLUXNET/Fluxnet_grid_european_applications.txt",
  header = TRUE,
  sep = "\t",
  quote = "\"",
  stringsAsFactors = FALSE
)

FLUXNET_grid <- FLUXNET_grid[FLUXNET_grid$Code != "IT-La2", ]
# Merge By Station name in ICOS Data      
merged_data <- merge(all_Fields_list[[1]]@data, FLUXNET_grid, 
                                by = c("Code", "Name"), 
                                all = TRUE)

merged_data[, `:=`(
  Lat = GUESS_Lat,
  Lon = GUESS_Lon
)]

all_Fields_list[[1]]@data <- merged_data[!is.na(Lat) & !is.na(Lon)]

this_benchmark@datasets[[1]]@data <- all_Fields_list[[1]]@data

 #all_Fields_list[[2]]@data <- all_Fields_list[[2]]@data[!( (Lat == 42.25 & Lon == 116.25)), ]
 lats <- unique(all_Fields_list[[1]]@data$Lat)
 lons <- unique(all_Fields_list[[1]]@data$Lon)

## Make comparison objects from your fields, used for comparison only!
all_comparisons <- DGVMBenchmarks::fullTemporalComparison(benchmark = this_benchmark, all_ts = all_Fields_list,       new_model = all_sim_full[[1]]@source@name)
plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"joined")
#plotFLUXNETFields(this_benchmark,all_Fields_list,all_comparisons,"per_source")
## Extracts statistical metrics from your fields.
if(length(this_benchmark@datasets) != 0){FLUXNET_table <- rbind(FLUXNET_table,
                     DGVMBenchmarks::makeMetricTable(benchmark = this_benchmark,
                                      all_comparisons_list = all_comparisons,
                                      simulation_sources = all_simulation_Sources_list))}
}
```


## Reco Daily Difference
```{r Difference Flux Reco, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=18, fig.height=14}
if (do_FLUXNET_Reco){plotAllTemporalComparisons(this_benchmark,all_comparisons)}
```


## Reco per site
```{r per site flux Reco, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=16, fig.height=12}
if (do_FLUXNET_Reco){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="station")}
```

## Reco per Land cover
```{r per lc flux Reco, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.width=14, fig.height=10}
if (do_FLUXNET_Reco){plotFLUXNETScatter(this_benchmark,all_comparisons,fill="landcover")}
```



# FLUXNET metric table
```{r FLUXNET Metric table, echo=FALSE, message=FALSE, warning=FALSE}
if(nrow(FLUXNET_table) > 0) {
   #substitute "r2" for something prettier in the "Metric" column
  FLUXNET_table$Metric <- gsub(pattern = "r2", replacement = "R^2^", FLUXNET_table$Metric)
  
   #print the table
  kable(FLUXNET_table) %>% kable_styling(full_width = TRUE)}
```





# Timing
Total run time:
``` {r time,echo=FALSE,message=FALSE}
# report total run time
toc()
```
